---
title: "FPA-SVR Report **"
params:
  C: NA
  ModelFit: NA
  eps: NA
  gamma: NA
  lag: NA
  mydataFrame: NA
  sv: NA
  var: NA
output:
  html_document:
    theme: "flatly"
    css: custom.css
---





```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



This is a report of forecasting using FPA-SVR method.


####1. Model Evaluation Result

Name           | Value
---------------|---------------
Variable       | <b>`r params$var`</b>
Method         | FPA-SVR
Kernel         | Radial
Lag            | `r params$lag`
Included Obs. (train)  | `r length(params$ModelFit$fitted)`
Number of SV   | `r params$sv`
| | |
<b>SVR paramseter</b> | |
C              | <b>`r params$C`</b>
gamma          | <b>`r params$gamma`</b>
eps            | <b>`r params$eps`</b>
| | |
<b>Accuracy Measure (Training set)</b> | |
Mean Absolute Scaled Error (MASE) | `r params$ModelFit$maseTrain`
Mean Absolute Percentage Error(MAPE) | `r params$ModelFit$mapeTrain`
Root Mean Squared Error (RMSE) | `r params$ModelFit$RMSETrain`
| | |
<b>Accuracy Measure (Test set)</b> | |
Mean Absolute Scaled Error (MASE) | `r params$ModelFit$maseTest`
Mean Absolute Percentage Error(MAPE) | `r params$ModelFit$mapeTest`
Root Mean Squared Error (RMSE) | `r params$ModelFit$RMSETest`

\pagebreak
<br>
<br>


####2. Forecasting plot
```{r, echo=F,fig.width=6}
 require(dygraphs)
 dygraph(params$mydataFrame)  %>%
        dySeries("trainingSet", color = "black") %>%
        dySeries("testSet", color = "grey") %>%
        dySeries("fitted", color = "blue") %>%
        dySeries("prediction", color = "red") 
```

<br></br>

####3. Forecasting value
```{r, echo=F}
  # params$mydataFrame 
  df <- sapply(params$mydataFrame, as.character)
  df[is.na(df)] <- " "
  
  knitr::kable(as.data.frame(df),row.names = T)
```
