##Forum Analisis Statistik
###Regression Report
###Tools: Geographically Weighted Ridge Regression
***






Raw data:
```{r kable, echo=FALSE}
 library(knitr)
 kable(hasilDataAwal()) 
```






Pemilihan Variabel:
```{r, echo=FALSE}
 hasilvarmetod()
```

Pengujian Autokorelasi dan Heterogenitas Spasial:
```{r kable2, echo=FALSE}
 library(knitr)
 kable(hasilidentifikasi()) 
```

#### Pemodelan Geographically Weighted Regression

```{r, echo=FALSE}
 bwgwr()
```

GWR Coefficients :
```{r kable3, echo=FALSE}
 library(knitr)
 kable(betagwr()) 
```

```{r, echo=FALSE}
 r2rmsegwr()
```


#####Hypothesis Testing
Goodness of Fits (GWR vs OLS)
```{r, echo=FALSE}
 gofgwr()
```

Simultan F test
```{r, echo=FALSE}
 simf()
```

Partial t test
```{r kable4, echo=FALSE}
 library(knitr)
 kable(partialtest()) 
```

All Possible Models
```{r kable5, echo=FALSE}
 library(knitr)
 kable(allposmod()) 
```

#### Identifikasi Multikolinieritas lokal dengan nilai VIF lokal

```{r kable6, echo=FALSE}
 library(knitr)
 kable(hasilviflokal())
 ketviflokal() 
```

#### Pemodelan Geographically Weighted Ridge Regression

```{r, echo=FALSE}
 bwgwrr()
```

GWRR Coefficients :
```{r kable7, echo=FALSE}
 library(knitr)
 kable(betagwrr()) 
```

```{r, echo=FALSE}
 r2rmsegwrr()
```


#####Hypothesis Testing

Simultan F test
```{r, echo=FALSE}
 simfgwrr()
```

Partial t test
```{r kable8, echo=FALSE}
 library(knitr)
 kable(partialtestgwrr()) 
```

All Possible Models
```{r kable9, echo=FALSE}
 library(knitr)
 kable(allposmodgwrr()) 
```
