##Forum Analisis Statistik
###Regression Report
###Tools: ANFIS
***

The Name of Model: 
```{r, echo=FALSE}
fsummary_modelname(doLearnFuzzy())
```

Model was Trained Using: 
```{r, echo=FALSE}
fsummary_modeltype(doLearnFuzzy())
```

The Names of Attributes:
```{r, echo=FALSE}
fsummary_variableattr(doLearnFuzzy())
```

The Interval of Training Data:
```{r, echo=FALSE}
fsummary_range_ori(doLearnFuzzy())
```

Type of Membership Functions: 
```{r, echo=FALSE}
fsummary_mffunction(doLearnFuzzy())
```

Type of T-norm Method:
```{r, echo=FALSE}
fsummary_tnormmethod(doLearnFuzzy())
```

Type of S-norm Method:
```{r, echo=FALSE}
fsummary_snormmethod(doLearnFuzzy())
```

Type of Implication Function: :
```{r, echo=FALSE}
fsummary_impfunc(doLearnFuzzy())
```

The Plot of Membership Function (normalized):
```{r, echo=FALSE}
plotMF(doLearnFuzzy())
```

The Parameter Values of Membership Function on the Input Variable (normalized) :
```{r, echo=FALSE}
fsummary_varinpmf(doLearnFuzzy())
```

The Fuzzy IF-THEN Rules:
```{r, echo=FALSE}
fsummary_ifthenrules(doLearnFuzzy())
```

The Linear Equations on Consequent Parts of Fuzzy IF-THEN Rules:
```{r, echo=FALSE}
fsummary_ifthenrulesconsequent(doLearnFuzzy())
```

Fitting and Predicting Plot:      
```{r plot, echo=FALSE}
getANFISfitPlotForSharing()
getANFISpredPlotForSharing()
```

Error and Residuals:
Fitting Phase
```{r, echo=FALSE}
getANFISResidualForSharingF()
```
Predicting Phase
```{r, echo=FALSE}
getANFISResidualForSharingP()
```

Predicted vs Real Value:
Fitting Phase
```{r, echo=FALSE}
getANFISRealvsPredF()
```
Predicting Phase
```{r, echo=FALSE}
getANFISRealvsPredP()
```